The Strucplot Framework:\\ Visualizing Multi-way Contingency Tables With \pkg{vcd}

### 2005-10-22 trunk/vcd/paper/JSS.Rnw
fixes
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@480 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
refs in datasets fixed.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@481 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{description}
\item[Titanic] Information on the fate of passengers on
  the fatal maiden voyage of the ocean liner `Titanic', summarized
  according to economic status (class), gender (`Sex'), age and
  survival. The data were originally collected by the British Board of Trade
  in their investigation of the sinking. Source: FIXME. Available in base \proglang{R}.
\item[PreSex]  Data from Thornes \& Collard (1979), reported in Gilbert (1981), on
  pre- and extra-marital sex and divorce. Source: FIXME. Available
  in the \pkg{vcd} package.
\item[Arthritis] Data from \cite{vcd:Koch+Edwards:1988} from a double-blind clinical trial
  investigating a new treatment for rheumatoid arthritis. Available
  in the \pkg{vcd} package.
\item[UCBAdmissions] Aggregate data on applicants to graduate school at Berkeley for
  the six largest departments in 1973 classified by admission and
  gender. Source: \cite{vcd:Bickel+Hammel+O'Connell:1975}. Available
  in base \proglang{R}.
\item[HairEyeColor] Distribution of hair and eye color and gender in 592 statistics
  students. The gender information is artificial. Source: \cite{vcd:Snee:1974}.
  Available in base \proglang{R}.
\item[Bundesliga] Results from the first German soccer league in the
  years 1995/6 \citep{vcd:Knorr-Held:1999} and 2001/2 (Achim
  Zeileis). Available in the \pkg{vcd} package.
\end{description}

>>>>

\begin{description}
\item[Arthritis] Data from \cite{vcd:Koch+Edwards:1988} from a double-blind clinical trial
  investigating a new treatment for rheumatoid arthritis. Available
  in the \pkg{vcd} package.
\item[Bundesliga] Results from the first German soccer league in the
  years 1995/6 \citep{vcd:Knorr-Held:1999} and 2001/2 (Achim
  Zeileis). Available in the \pkg{vcd} package.
\item[HairEyeColor] Distribution of hair and eye color and gender in 592 statistics
  students. The gender information is artificial. Source: \cite{vcd:Snee:1974}.
  Available in base \proglang{R}.
\item[PreSex]  Data from \cite{vcd:thornes+collard:1979} reported in 
  \cite{vcd:gilbert:1981}, on pre- and extra-marital sex and divorce. Available
  in the \pkg{vcd} package.
\item[Titanic] Information on the fate of passengers on
  the fatal maiden voyage of the ocean liner `Titanic', summarized
  according to economic status (class), gender (`Sex'), age and
  survival.  Source: \cite{vcd:dawson:1995} (Data 
  originally collected by the British Board of Trade
  in their investigation of the sinking). Available in base \proglang{R}.
\item[UCBAdmissions] Aggregate data on applicants to graduate school at Berkeley for
  the six largest departments in 1973 classified by admission and
  gender. Source: \cite{vcd:Bickel+Hammel+O'Connell:1975}. Available
  in base \proglang{R}.
\end{description}
